Stability and accuracy of free surface time integration in buoyancy driven viscous flows

### 2016-04-28 free-surface-paper.tex
Fix typo.
Try on a new title.

\title{Free surface computations in mantle convection models}

@@

\begin{itemize}
\item Direct solution of Equation~\eqref{eq:generalized_eigenvalue}. This can be expensive, although
only the minimun relaxation time is required. For certain geometries a simple power iteration on 
the standard eigenvalue problem (Equation~\eqref{eq:standard_eigenvalue}) could be enough.
\item Analytical formulae. Several geometry and viscosity model combinations have analytical solutions
for relaxation spectra. Even if the user's model is not precisely the same (e.g., has some lateral viscosity
variations), an analytical approximation may be sufficient.
\item Scaling. In general, we expect the relaxation times to scale with $\tau \sim \frac{\eta}{\rho g L}$,
where the density, gravity, viscosity, and lengthscale $L$ are all representative values.  A small amount
of experimentation near this value of $\tau$ can find an appropriate relaxation time.
\item Observation of instabilities.  The mere act of observing a sloshing instability in an unstabilized
problem can furnish an estimate of its relaxation time.
\end{itemize}

>>>>

\title{Stability and accuracy of free surface time integration in buoyancy driven viscous flows}

@@

\begin{itemize}
\item Direct solution of Equation~\eqref{eq:generalized_eigenvalue}. This can be expensive, although
only the minimum relaxation time is required. For certain geometries a simple power iteration on 
the standard eigenvalue problem (Equation~\eqref{eq:standard_eigenvalue}) could be enough.
\item Analytical formulae. Several geometry and viscosity model combinations have analytical solutions
for relaxation spectra. Even if the user's model is not precisely the same (e.g., has some lateral viscosity
variations), an analytical approximation may be sufficient.
\item Scaling. In general, we expect the relaxation times to scale with $\tau \sim \frac{\eta}{\rho g L}$,
where the density, gravity, viscosity, and lengthscale $L$ are all representative values.  A small amount
of experimentation near this value of $\tau$ can find an appropriate relaxation time.
\item Observation of instabilities.  The mere act of observing a sloshing instability in an unstabilized
problem can furnish an estimate of its relaxation time.
\end{itemize}
